---
title: "MAD Project Analysis"
author: "Anirudh"
date: "5/19/2020"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
runtime: shiny
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# VERSIONS 

/********************** V2 FEATURES *****************************/
-- CROSS CHAT SCORING GRAPH [OVER ALL -USING AFINN (MAIN) / BING (SUPPORT)]
-- SENTIMENT ANALYSIS GRAPH [OVER ALL -USING NRC]
-- STATISTICS [OVER ALL -USING AFINN (MAIN) / BING (SUPPORT)] (chatid | Negative_perc | Positive_perc | negative_angle_index | anger)

/********************** V4 FEATURES *****************************/
-- CROSS CHAT SCORING GRAPH [BOT/USER -USING AFINN]
-- CROSS CHAT SCORING GRAPH [BOT/USER -USING BING]
-- CROSS CHAT (CHUNK) SCORING GRAPH [BOT/USER -USING AFINN]
-- CROSS CHAT (CHUNK) SCORING GRAPH [BOT/USER -USING BING]
-- SENTIMENT ANALYSIS GRAPH [BOT/USER -USING NRC]
-- SENTIMENT ANALYSIS GRAPH [BOT/USER -USING BING]
-- STATISTICS [USER ONLY -USING AFINN] (chatid | Negative_perc | Positive_perc | negative_angle_index | anger)
-- STATISTICS [OVER ALL -USING AFINN] (chatid | change_in_negative_angle)


# LOAD LIBRARY

```{r}
library(tidyverse)
library(dplyr)
library(tidytext)
library(ggplot2)
library(gutenbergr)
library(scales)
library(stringr)
library(tidyr)
library(wordcloud)
library(reshape2)
library(forcats)
library(igraph)
library(ggraph)
library(widyr)
library(tm)
library(topicmodels)
library(quanteda)
library(Matrix)
library(tm.plugin.webmining)
library(purrr)
library(scales)
library(mallet)
library(rjson)
library(shiny)
library(DT) 
library(corrr)
library(flexdashboard)
library(shiny)
library(shinydashboard)
```

# SETUP INITIAL CONFIGURATION

```{r}
do_uni_gram <- FALSE

do_multi_gram <- TRUE
n_gram_size <- 2

do_chunk_perc <- TRUE
perc_value <- 20

remove_stopwords <-  TRUE

remove_negation <- TRUE
negation_words <- c("not", "no", "never", "without")
```

# IMPORT DATA

### Import data -> Store in tibble -> General Cleanup
```{r}
#Import
actual_data <- read.csv("Data\\controlset.csv",encoding = "UTF-8")

#Load to tibble
actual_data <-  as.tibble(actual_data)

#Clean up
actual_data <- actual_data %>% rename(chatid=`X.U.FEFF.chatid`)
```

# TOKENIZE

```{r}
#TOKENIZE
if(do_uni_gram)
{
  tidy_data <- actual_data %>%  unnest_tokens(word, text)
}
if(do_multi_gram)
{
  tidy_data <- actual_data %>%  
    unnest_tokens(multi_gram,text,token ="ngrams",n=n_gram_size) %>% 
    separate(multi_gram,into = c("word1","word"),sep=" ") %>%
    filter(!is.na(word),!grepl("[[:digit:]]",word))
}

```

# FILTER STOP AND NEGATION WORDS

```{r}
if(remove_stopwords)
{
  data(stop_words)
  tidy_data <- tidy_data %>%
  anti_join(stop_words,by = c("word"="word"))
}

#Setup Negation Flag and Filter
if(remove_negation)
{
  tidy_data <- tidy_data %>%  mutate(negate_flg=if_else(word1 %in% negation_words,"1","0"))
  tidy_data <-  tidy_data %>%  filter(negate_flg==0)
}
```

# INITIALIZE AND APPPLY LEIXCONS

**About:**

1. Affin lexicon scale: -5 to +5 , it specifies the degree of negativity

2. Bing lexicon scale: Postive or Negative, it does not have a scale, just mentions if a word is negative or positive

3. NRC lexicon scale: Anger,Trust,Fear....10 in total, mentions what a emotion a word represents.

**Note:**

1. NRC lexicon will be specifically used in "sentiment analysis plotting" and not "across-chat negative-positive scoring plot" as it specifically is designed for emotion interpretation

2. Affin lexicon will be specifically used in plotting "across-chat negative-positive scoring plot" and overall conversation scoring

3. Since there may be words present in Bing lexicon that may not be present in Affin lexicons, we will be using standardized average positive/negative score from Affin Lexicons (Avg negative score: -2.06 & Avg postive score: 2.08) in conjunction with Bing to improve the overall interpretation

```{r}
afinn_lex <- get_sentiments("afinn")
bing_lex <- get_sentiments("bing")
nrc_lex <- get_sentiments("nrc")


tidy_data_scoring <- tidy_data %>% 
  left_join(afinn_lex) %>% 
  rename(afinn_sentiment=value) %>% 
  left_join(bing_lex) %>% 
  rename(bing_sentiment=sentiment) #%>%
  #mutate(bing_sentiment=ifelse(bing_sentiment=="positive",2.08,ifelse(bing_sentiment=="negative",-2.06,NA))) 
              

tidy_data_nrc <- tidy_data %>% 
              inner_join(nrc_lex) %>% 
              rename(nrc_sentiment=sentiment) 
```

# Perform Sentiment Analysis

```{r}
tidy_data_sentiment <- tidy_data_nrc %>% 
  group_by(chatid,user,nrc_sentiment) %>% 
  summarise(count=n()) %>% 
  ungroup() %>%  
  pivot_wider(names_from = nrc_sentiment,values_from = count) %>% 
  replace(.,is.na(.),0)

tidy_data_sentiment <-  tidy_data_sentiment %>% 
  mutate(Total_words_scored=apply(tidy_data_sentiment[3:12],1,sum)) %>% 
  mutate(anticipation=anticipation/Total_words_scored*100,
        joy=joy/Total_words_scored*100,
        positive=positive/Total_words_scored*100,
        trust=trust/Total_words_scored*100,
        surprise=surprise/Total_words_scored*100,
        anger=anger/Total_words_scored*100,
        disgust=disgust/Total_words_scored*100,
        fear=fear/Total_words_scored*100,
        negative=negative/Total_words_scored*100,
        sadness=sadness/Total_words_scored*100)

tidy_data_sentiment_bing <-  tidy_data_scoring %>% 
                              filter(!is.na(bing_sentiment)) %>% 
                              group_by(chatid,user,bing_sentiment) %>% 
                              count() %>% 
                              ungroup() %>% 
                              pivot_wider(names_from = bing_sentiment,values_from = n) %>% 
                              replace(.,is.na(.),0) %>% mutate(Total_words_scored=positive+negative) %>%
                              mutate(positive=positive/Total_words_scored*100,negative=negative/Total_words_scored*100)
```

# Cross-Chat scoring

```{r}
#Calculating overall score, i.e., words for which afinn score is not available, we are replacing it with earlier calculated bing score
tidy_data_scoring <- tidy_data_scoring %>% 
  mutate(overall_score=afinn_sentiment)

#Cross Chat Scoring
tidy_data_cross_chat <- tidy_data_scoring  %>% 
  filter(!is.na(overall_score)) %>% 
  group_by(chatid,chatorder,user)  %>%  
  summarise(per_message_score=mean(overall_score)) %>% 
  ungroup()

tidy_data_cross_chat_bing <- tidy_data_scoring  %>% 
  filter(!is.na(bing_sentiment)) %>% 
  group_by(chatid,chatorder,user)  %>%
  mutate(bing_sentiment=ifelse(bing_sentiment=="postive",1,-1)) %>% 
  summarise(per_message_score=sum(bing_sentiment)) %>% 
  ungroup()

#Adding 0 at chat order 1 to chats with no scoring on 1st message for better visual appeal in the graph
tidy_data_cross_chat <- tidy_data_cross_chat %>% 
  union_all(
    tidy_data_cross_chat %>% 
    group_by(chatid) %>% 
      summarise(chatorder=min(chatorder)) %>% 
      filter(chatorder>1) %>% 
      mutate(chatorder=as.integer(1),per_message_score=0))

tidy_data_cross_chat_bing <- tidy_data_cross_chat_bing%>% 
  union_all(
    tidy_data_cross_chat_bing %>% 
    group_by(chatid) %>% 
      summarise(chatorder=min(chatorder)) %>% 
      filter(chatorder>1) %>% 
      mutate(chatorder=as.integer(1),per_message_score=0))

```

# Overall Scoring

### Overall scoring is consist of three sections

1. We will show the overall negative and postive content percentage per chat based on scoring

2. We shall run a linear regression model, wherein chat order is our predictor and per message score in individual chats is the dependent variable. From this we are trying to acheive negative rate index.

3. We will append the anger % per chat to the overall scoring tibble by join sentiment data

***Note***

We are running the linear regresion model for only one purpose. To get the slope. We are not interested in p-value or predictions. The slope of the best fitted line will help up determine if the conversation is progressing in a negative or postive manner.

***Negative Rate Index***

An index that specfies if a conversation is heading into a negative tone. The scale lies between -90 to +90. Where Anthying over 0 is bad, indicating the chat going into a negative context. Higher the number higher the risk. Values under 0 state that the conversation might have had a bad start, but the bot was able to bring it to a positive end.

```{r}


#Over all Chat Scoring
tidy_data_overall_scoring <- tidy_data_scoring  %>%
  filter(!is.na(overall_score)) %>% 
  mutate(score_type=ifelse(overall_score>0,"Positive","Negative")) %>% 
  group_by(chatid,user,score_type)  %>%  
  summarise(overall_score=sum(overall_score)) %>% 
  pivot_wider(names_from = score_type,values_from = overall_score) %>% 
  replace(.,is.na(.),0) %>% 
  mutate(Total_words_scored=abs(Negative)+Positive) %>%
  mutate(Negative_perc=abs(Negative)/Total_words_scored*100,Positive_perc=Positive/Total_words_scored*100) %>% 
  arrange(desc(Negative_perc))

#Creating Linear Model to get the best fitted line slope
tidy_data_LM_model <- tidy_data_scoring  %>% 
  filter(!is.na(overall_score)) %>% 
  group_by(chatid,user,chatorder)  %>%  
  summarise(per_message_score=mean(overall_score)) %>% 
  ungroup() 

#Append details with overall scoring tibble
tidy_data_overall_scoring <- tidy_data_overall_scoring %>% add_column(slope = 0)

model_for <-  per_message_score ~ chatorder

for(i in  tidy_data_LM_model %>% distinct(chatid)%>%  pull(chatid) )
{
  for(usr in tidy_data_LM_model %>% filter(chatid==i) %>% distinct(user) %>% pull(user))
  {
    dat <- tidy_data_LM_model %>% filter(chatid==i & user==usr)
    if(dat %>% summarise(n_distinct(chatorder)) > 2 )
      {
      slope_model <- lm(model_for, data = dat)
      tidy_data_overall_scoring <- tidy_data_overall_scoring %>%
        mutate(slope=ifelse(chatid==i & user==usr,signif(slope_model$coef[[2]], 2),slope))
      }
  }
  
}

#find angle and set negative rate index (rate at which negativity is increasing across a chat, higher number higher the negativity increase in chat)
tidy_data_overall_scoring <- tidy_data_overall_scoring %>% mutate(angle=as.integer(atan(slope)*180/pi),negative_rate_index=-1*angle)

tidy_data_overall_scoring <- tidy_data_overall_scoring %>% left_join(tidy_data_sentiment %>% select(chatid,user,anger),by = c("chatid"="chatid","user"="user"))

#write.csv(anger,file="Bkp\\anger.csv")
#save(tidy_data_summary,file="Bkp\\Google_conv_tidy_data_summary.rda")
```

# Plot graphs

```{r eval=FALSE}
tidy_data_overall_scoring %>% filter(user!="Bot") %>%  select(chatid,Total_words_scored,Positive_perc,Negative_perc,negative_rate_index,anger) %>% print(nrow(20))

if(do_chunk_perc)
{
  actual_data_chunked <- actual_data %>% group_by(chatid) %>% summarise(msg_cnt=n_distinct(chatorder),chunk_size=round(msg_cnt*perc_value/100))
  
  tidy_data_cross_chat %>% 
  filter(chatid==10 & !is.na(user)) %>% 
    left_join(actual_data_chunked, by = ("chatid"="chatid")) %>% 
    mutate(chunk_order=ceiling(chatorder/chunk_size)) %>% 
    group_by(chunk_order) %>% 
    summarise(per_message_score=mean(per_message_score)) %>% 
    ungroup() %>% 
     ggplot() +
  geom_line(mapping =  aes(x=chunk_order,y=per_message_score),color='red')+
  geom_point(mapping =  aes(x=chunk_order,y=per_message_score),color='black')+
  #geom_smooth(mapping =  aes(x=chatorder,y=per_message_score),se = F,color='black')+
  geom_hline(yintercept =0,color="blue")+
  theme(text = element_text(color = "lightseagreen"),strip.text=element_text( colour="navy")) +
  ggplot2::annotate("text",x=3,y=4, label= "Postive Context")+
  ggplot2::annotate("text",x=3,y=-4, label= "Negative Context")+
  ylim(-5,5)+
  ggtitle(paste("CROSS CHAT -AFFFIN SCORE [CHUNK Split :",perc_value,"%]"))
  
  tidy_data_cross_chat_bing %>% 
  filter(chatid==10 & !is.na(user)) %>% 
    left_join(actual_data_chunked, by = ("chatid"="chatid")) %>% 
    mutate(chunk_order=ceiling(chatorder/chunk_size)) %>% 
    group_by(chunk_order) %>% 
    summarise(per_message_score=sum(per_message_score)) %>% 
    ungroup() %>% 
     ggplot() +
  geom_line(mapping =  aes(x=chunk_order,y=per_message_score),color='red')+
  geom_point(mapping =  aes(x=chunk_order,y=per_message_score),color='black')+
  #geom_smooth(mapping =  aes(x=chatorder,y=per_message_score),se = F,color='black')+
  geom_hline(yintercept =0,color="blue")+
  theme(text = element_text(color = "lightseagreen"),strip.text=element_text( colour="navy")) +
  ggplot2::annotate("text",x=3,y=4, label= "Postive Context")+
  ggplot2::annotate("text",x=3,y=-4, label= "Negative Context")+
  ggtitle(paste("CROSS CHAT -BING SCORE [CHUNK Split :",perc_value,"%]"))
  
  tidy_data_chunk_slope  <- tidy_data_cross_chat %>% 
  filter(!is.na(user)) %>% 
      group_by(chatid) %>% 
    left_join(actual_data_chunked, by = ("chatid"="chatid")) %>% 
    mutate(chunk_order=ceiling(chatorder/chunk_size)) %>% 
      filter(n_distinct(chunk_order)>2) %>% 
    group_by(chatid,chunk_order) %>% 
    summarise(per_message_score=mean(per_message_score)) %>% 
      mutate(curr_slope=round(lm(per_message_score ~ chunk_order)$coeff[[2]],2)) %>% 
      filter(chunk_order!=max(chunk_order)) %>% 
      mutate(last_slope=round(lm(per_message_score ~ chunk_order)$coeff[[2]],2)) %>% 
      mutate(slope_change=curr_slope-last_slope) %>% 
      distinct(chatid,slope_change) %>% 
    mutate(angle_chunk=as.integer(atan(slope_change)*180/pi),negative_rate_chunk=-1*angle_chunk)
    
actual_data_chunked %>% left_join(tidy_data_chunk_slope,by = c("chatid"="chatid")) %>% replace(.,is.na(.),0)


}
tidy_data_cross_chat %>% 
  filter(chatid==11 & !is.na(user)) %>% 
  ggplot() +
  geom_line(mapping =  aes(x=chatorder,y=per_message_score),color='red')+
  geom_point(mapping =  aes(x=chatorder,y=per_message_score),color='black')+
  #geom_smooth(mapping =  aes(x=chatorder,y=per_message_score),se = F,color='black')+
  geom_hline(yintercept =0,color="blue")+
  theme(text = element_text(color = "lightseagreen"),strip.text=element_text( colour="navy")) +
  ggplot2::annotate("text",x=3,y=4, label= "Postive Context")+
  ggplot2::annotate("text",x=3,y=-4, label= "Negative Context")+
  ylim(-5,5)+
  facet_wrap(~user,ncol = 1)+
  ggtitle("CROSS CHAT -AFFFIN SCORE")

 tidy_data_cross_chat %>% 
filter(chatid==11 & !is.na(user)) %>% 
   plot_ly(x=~chatorder[user!="Bot"],y=~per_message_score[user!="Bot"],type = "scatter",mode="line",name="User") %>%
   add_trace(x=~chatorder[user=="Bot"],y=~per_message_score[user=="Bot"],type = "scatter",mode="line",name="Bot") %>%
   layout(title="CROSS CHAT -AFFFIN SCORE",xaxis=list(title="Chat Order",dtick=1),yaxis=list(title="Score",range=c(-5,5),dtick=1)) %>% 
   add_annotations(xref="paper",yref="paper",x=0.5,y=0.85,text="Postive Context",showarrow=F) %>% 
   add_annotations(xref="paper",yref="paper",x=0.5,y=0.15,text="Negative Context",showarrow=F)

tidy_data_cross_chat_bing %>% 
  filter(chatid==11 & !is.na(user)) %>% 
  ggplot() +
  geom_line(mapping =  aes(x=chatorder,y=per_message_score),color='red')+
  geom_point(mapping =  aes(x=chatorder,y=per_message_score),color='black')+
  #geom_smooth(mapping =  aes(x=chatorder,y=per_message_score),se = F,color='black')+
  geom_hline(yintercept =0,color="blue")+
  theme(text = element_text(color = "lightseagreen"),strip.text=element_text( colour="navy")) +
  ggplot2::annotate("text",x=3,y=4, label= "Postive Context")+
  ggplot2::annotate("text",x=3,y=-4, label= "Negative Context")+
  facet_wrap(~user,ncol = 1)+
  ggtitle("CROSS CHAT -BING SCORE")

 tidy_data_cross_chat_bing %>% 
  filter(chatid==11 & !is.na(user)) %>% 
   plot_ly(x=~chatorder[user!="Bot"],y=~per_message_score[user!="Bot"],type = "scatter",mode="line",name="User") %>%
   add_trace(x=~chatorder[user=="Bot"],y=~per_message_score[user=="Bot"],type = "scatter",mode="line",name="Bot") %>%
   layout(title="CROSS CHAT -BING SCORE",xaxis=list(title="Chat Order",dtick=1),yaxis=list(title="Score",range=c(-5,5),dtick=1)) %>% 
   add_annotations(xref="paper",yref="paper",x=0.5,y=0.85,text="Postive Context",showarrow=F) %>% 
   add_annotations(xref="paper",yref="paper",x=0.5,y=0.15,text="Negative Context",showarrow=F)

tidy_data_sentiment %>% 
  select(-Total_words_scored) %>% 
  filter(chatid==11) %>% 
  pivot_longer(c(-chatid,-user),names_to = "emotion",values_to = "score") %>% 
  ggplot()+
  geom_bar(mapping = aes(x=emotion,y=score,fill=emotion),stat = "identity",show.legend =F)+
  coord_flip() +
  facet_wrap(~user)+
  ggtitle("SENTIMENT CHART -NRC SCORE")

 tidy_data_sentiment %>% 
  select(-Total_words_scored) %>% 
  filter(chatid==11) %>%  
  pivot_longer(c(-chatid,-user),names_to = "emotion",values_to = "score") %>% 
   plot_ly(x=~score[user!="Bot"],y=~emotion[user!="Bot"],type = "bar",name="User",orientation = 'h') %>%
   add_trace(x=~score[user=="Bot"],y=~emotion[user=="Bot"],type = "bar",name="Bot") %>% 
   layout(title="SENTIMENT CHART -NRC SCORE",xaxis=list(title="Score"),yaxis=list(title="Emotion")) 
 
tidy_data_sentiment_bing %>% 
  select(-Total_words_scored) %>% 
  filter(chatid==11) %>% 
  pivot_longer(c(-chatid,-user),names_to = "emotion",values_to = "score") %>% 
  ggplot()+
  geom_bar(mapping = aes(x=emotion,y=score,fill=emotion),stat = "identity",show.legend =F)+
  coord_flip() +
  facet_wrap(~user)+
  ggtitle("SENTIMENT CHART -BING SCORE")

 tidy_data_sentiment_bing %>% 
  select(-Total_words_scored) %>% 
  filter(chatid==11) %>%  
  pivot_longer(c(-chatid,-user),names_to = "emotion",values_to = "score") %>% 
   plot_ly(x=~score[user!="Bot"],y=~emotion[user!="Bot"],type = "bar",name="User",orientation = 'h') %>%
   add_trace(x=~score[user=="Bot"],y=~emotion[user=="Bot"],type = "bar",name="Bot") %>% 
   layout(title="SENTIMENT CHART -BING SCORE",xaxis=list(title="Score"),yaxis=list(title="Emotion")) 


tidy_data_idf <-  tidy_data %>% group_by(chatid,word) %>% count() %>% bind_tf_idf(word,chatid,n) %>% ungroup()

g <- tidy_data_idf %>% 
  mutate(chatid=as.factor(chatid)) %>% 
  group_by(chatid) %>% 
  top_n(2,tf_idf) %>% 
  ungroup() %>% 
  mutate(word=reorder(word,tf_idf)) %>% 
  ggplot(aes(word,tf_idf,fill=chatid)) + 
  geom_col(show.legend = F) + 
  labs(x = NULL, y = "tf-idf score") +
  facet_wrap(~chatid,scales ="free" ) + 
  coord_flip()

ggplotly(g)

tidy_data_dfm <- tidy_data %>% count(chatid,word,sort = T) %>% cast_dfm(chatid,word,n)

tidy_data_topicmodel <- stm(tidy_data_dfm,K = 5,init.type = "Spectral")

tidy_beta <- tidy(tidy_data_topicmodel)

tidy_beta %>% group_by(topic) %>% 
  top_n((10)) %>% 
  ungroup() %>% 
  mutate(term = reorder(term,beta)) %>% 
  ggplot(aes(term,beta,fill=topic))+
  geom_col(show.legend = F)+
  facet_wrap(~topic,scales = "free")+
  coord_flip()
```

# Testing code - Ignore

```{r eval=FALSE}
actual_data %>% filter(chatid==10) %>% select(user,text)
tidy_data_scoring %>%  filter(!is.na(overall_score),chatid==10,user=="James") %>% arrange(chatorder) %>% print(n=100) 
tidy_data_scoring %>%  filter(!is.na(overall_score),chatid==5) %>% arrange(chatorder) %>% print(n=100) 
tidy_data_nrc %>%  filter(chatid==5) %>% arrange(nrc_sentiment) %>%  print(n=100) 

#Important Linear model testing code
model_for <-  per_message_score ~ chatorder
dat <- tidy_data_LM_model %>% filter(chatid==3)
fit1 <- lm(model_for, data = dat)
ggplotRegression(fit1)

ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))+
  ylim(-5,5)

}

tidy_data_cross_chat %>% 
  filter(!is.na(user),chatid==10) %>% 
    left_join(actual_data_chunked, by = ("chatid"="chatid")) %>% 
    mutate(chunk_order=ceiling(chatorder/chunk_size)) %>% 
      filter(n_distinct(chunk_order)>2) %>% 
    group_by(chatid,chunk_order) %>% 
    summarise(per_message_score=mean(per_message_score)) %>% 
      mutate(curr_slope=round(lm(per_message_score ~ chunk_order)$coeff[[2]],2)) %>% 
      filter(chunk_order!=max(chunk_order)) %>% 
      mutate(last_slope=round(lm(per_message_score ~ chunk_order)$coeff[[2]],2)) %>% 
      mutate(slope_change=curr_slope-last_slope) %>% 
      distinct(chatid,slope_change) %>% 
    mutate(angle_chunk=as.integer(atan(slope_change)*180/pi),negative_rate_chunk=-1*angle_chunk)

tidy_data %>% select(chatid,user,word) %>% nest(words=c(word))

tidy_data %>% select(chatid,word) %>% count(chatid,word) %>% cast_sparse(chatid,word,n)

# Create dummy data
A <- B <- C <- sample(1:20, size = 20, replace = TRUE)
ID <- sort(rep(seq(1:4), 5))
Data <- data.frame(ID, A, B, C)

# Lead the variable by two time units

library(slider)

tidy_data_nested <-  tidy_data %>% select(chatid,word) %>% nest(words=c(word))

test  <- tidy_data_nested %>% filter(chatid==1) %>% select(words) %>% unnest()

skipgrams <- slider::slide(test,~.x,.after = 3,.step = 1,.complete = T) %>% view()
safe_mutate <- safely(mutate)
out <- map2(skipgrams,1:length(skipgrams),~safe_mutate(.x,window_id=.y))

t1 <- out %>% transpose() %>% pluck("result") %>% compact() %>% bind_rows()

t1 %>% filter(word %in% c("product","assist","understand","situation","share","id","glad")) %>% view()

  t1 %>% pairwise_pmi(word,window_id) %>% filter((item1=="product" & item2 %in% c("product","sir","understand","situation"))|(item2=="product" & item1 %in% c("product","sir","understand","situation")))

   t1 %>% pairwise_pmi(word,window_id) %>% filter((item1=="glad" & item2 %in% c("product","assist","understand","situation","share","id"))|(item2=="glad" & item1 %in% c("product","assist","understand","situation","share","id"))) %>% arrange(pmi)
  
#Higher the number better and closer is the relation, also influenced by overall occurance of word in different windows. More unique it appears higher the score.
   
slider::slide(1:4, ~.x)

# Plotly

library(plotly)

s <- seq(-1, 4, by = 0.25)

#layout config
a <- list(
  zeroline = TRUE,# zero axis lines
  zerolinecolor = toRGB("red"),
  zerolinewidth = 4,
  showline = TRUE,# x axis and y axis line
  linecolor = toRGB("black"),
  linewidth = 6,
  mirror = "ticks",# mirror entire x and y lines
  showgrid = T,
  gridcolor = toRGB("gray50"),#grid lines
  gridwidth = 2,#grid lines
  #autorange = "reversed", # reverse the axis
  #range = c(10, 0),
  #type="log", #scale type
  #type = 'bar',
  autotick = T, # ticks on x and y axis
  ticks = "outside",
  tick0 = 0,
  dtick = 0.25,
  ticklen = 5,
  tickwidth = 2,
  tickcolor = toRGB("red")
)

plot_ly(x = ~s, y = ~s) %>% layout(xaxis = a, yaxis = a) %>% add_markers() %>% add_markers(y = ~rev(s)) %>% add_trace(y = ~exp(s),name = "exp")

plot_ly(
    x = c('A12', 'BC2', 109, '12F', 215, 304),
    y = c(1,6,3,5,1,4),
    type = 'bar',
    name = 'Team A',
    text = c('Apples', 'Pears', 'Peaches', 'Bananas', 'Pineapples', 'Cherries'),
    orientation='h'
  ) %>% layout(
    title = 'Inventory',
    xaxis = list(
      type = 'category',
      title = 'Product Code'
    ),
    yaxis = list(
      title = '# of Items in Stock',
      range = c(0,7)
    )
  )

plot_ly(orientation='h', line=list(color='gray'), height=400, width=600) %>% add_boxplot(x=c(2,3,1,5), y=c('A','A','A','A'), name='A') %>% add_boxplot(x=c(8,3,6,5), y=c('B','B','B','B'), name='B')  %>% add_boxplot(x=c(2,3,2,5), y=c('C','C','C','C'), name='C') %>% add_boxplot(x=c(7.5,3,6,4), y=c('D','D','D','D'), name='D') %>% layout(
    title = '',
    yaxis = list(
      autorange = TRUE, 
      categoryorder = "category descending", 
      domain = c(0, 1), 
      range = c(-0.5, 3.5), 
      showline = TRUE, 
      title = "", 
      type = "category"
    ),
    margin = list(
      r = 10, 
      t = 25, 
      b = 40, 
      l = 110
    ), 
    legend = list(
      x = 0.986145833333, 
      y = 0.936263886049
    ),
    shapes = list(  #shapes and line embed
      list(
        line = list(
          color = "rgba(68, 68, 68, 0.5)", 
          width = 1
        ), 
        type = "line", 
        x0 = -0.3, 
        x1 = 1.2, 
        xref = "paper", 
        y0 = 0.5, 
        y1 = 0.5, 
        yref = "paper"
      ), 
      list(
        line = list(
          color = "rgba(68, 68, 68, 0.63)", 
          width = 1
        ), 
        type = "line", 
        x0 = -0.3, 
        x1 = 1.2, 
        xref = "paper", 
        y0 = 1, 
        y1 = 1, 
        yref = "paper"
      )
    ),
    annotations = list(  #text embed
        list(
          x = -0.0951769406393, 
          y = 1.06972670892, 
          showarrow = FALSE, 
          text = "Subgroup", 
          xref = "paper", 
          yref = "paper"
        ), 
        list(
          x = -0.235516552511, 
          y = 1.07060587474, 
          showarrow = FALSE, 
          text = "Group", 
          xref = "paper", 
          yref = "paper"
        ), 
        list(
          x = -0.235516552511, 
          y = 0.922906017856, 
          showarrow = FALSE, 
          text = "One", 
          xref = "paper", 
          yref = "paper"
        ), 
        list(
          x = -0.235516552511, 
          y = 0.375, 
          showarrow = FALSE, 
          text = "Two", 
          xref = "paper", 
          yref = "paper"
        )
      ))

plot_ly(
    width = 800,
    height = 500
  ) %>% add_trace(
    x = c(0,1,1,0,0,1,1,2,2,3,3,2,2,3),
    y = c(0,0,1,1,3,3,2,2,3,3,1,1,0,0),
    mode = 'lines'
  ) %>% add_trace(
    x = c(0,1,2,3),
    y = c(1,2,4,8),
    yaxis = "y2",
    mode = 'lines'
  ) %>% add_trace(
    x = c(1,10,100,10,1),
    y = c(0,1,2,3,4),
    xaxis = "x2",
    yaxis ="y3",
    mode = 'lines'
  ) %>% add_trace(
    x = c(1,100,30,80,1),
    y = c(1,1.5,2,2.5,3),
    xaxis = "x2",
    yaxis = "y4",
    mode = 'lines'
  ) %>% layout(
    title = "fixed-ratio axes",
    xaxis = list(
      nticks = 10,
      domain = c(0, 0.45),
      title = "shared X axis"
    ),
    yaxis = list(
      scaleanchor = "x",
      domain = c(0, 0.45),
      title = "1:1"
    ),
    yaxis2 = list(
      scaleanchor = "x",
      scaleratio = 0.2,
      domain = c(0.55,1),
      title = "1:5"
    ),
    xaxis2 = list(
      type = "log",
      domain = c(0.55, 1),
      anchor = "y3",
      title = "unconstrained log X"
    ),
    yaxis3 = list(
      domain = c(0, 0.45),
      anchor = "x2",
      title = "Scale matches ->"
    ),
    yaxis4 = list(
      scaleanchor = "y3",
      domain = c(0.55, 1),
      anchor = "x2",
      title = "Scale matches <-"
    ),
    showlegend= FALSE
)

plot_ly(x = seq(2, 6, by = 2), y = seq(-3, 3, by = 3)) %>% layout(
    xaxis = list(rangemode = "tozero"),
    yaxis = list(rangemode = "nonnegative"))


aggregate(mpg~cyl+hp,data = mtcars,mean)

```

```{r}

ui <- dashboardPage(
        dashboardHeader(title="MAD Dashboard"),
        dashboardSidebar(disable=T),
        dashboardBody
        (
          uiOutput("UITable")
        )
      )

server <- function(input, output) 
          {
            output$UITable <- renderUI({
                                box(width=12,
                                    lapply(1:nrow(tidy_data_overall_scoring), function(i) 
                                        {
                                          current_chatID <- tidy_data_overall_scoring[i,'chatid']
                                          neg <- round(tidy_data_overall_scoring[i,'Negative_perc'],2)
                                          neg_color <-ifelse(neg>=80,"red",ifelse(neg>=50&neg<80,"orange",ifelse(neg<=20,"blue","green")))
                                          rate <- tidy_data_overall_scoring[i,'negative_rate_index']
                                          rate_color <-ifelse(rate>=45,"red",ifelse(rate>=1&rate<45,"orange",ifelse(rate<=-45,"blue","green")))
                                          anger <- round(tidy_data_overall_scoring[i,'anger'],2)
                                          anger_color <-ifelse(anger>=10,"red",ifelse(anger>=5&anger<10,"orange","green"))
                                         box(title =paste("ChatID: ", current_chatID) , status = "primary", solidHeader = T, width = 12,
                                            fluidPage(fluidRow(
                                                column
                                                (
                                                12, offset = 0, style = 'padding:1px;',
                                                valueBox(neg,"Negativity",width=4,color =neg_color ),
                                                valueBox(rate,"Negativity Rate",width=4,color = rate_color),
                                                valueBox(anger,"Anger",width=4,color = anger_color)
                                                )
                                              )
                                            )
                                           )
                                        }
                                      )
                                    )
                                })
            }



shinyApp(ui = ui, server = server)

```



